\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{parskip}
%\usepackage{fullpage}
\begin{document}
\begin{center}
{\Huge\underline{SSL Project Overview} }
\vspace{20pt}

 {\Huge\textbf{BOOK WORLD} }
 \\
 \vspace{15pt}
\Large\textbf{Team 22}
\\
\vspace{20pt}
\begin{tabular}{l c}
      Rahul Raj &  (200010044) \\
     Manasa S& (200010058)\\
     Karthik K & (200010024) \\
     
\end{tabular}
\end{center}



\newpage


% \tableofcontents
\newpage
{\Large\textbf{BOOK WORLD}}
\begin{itemize}
\item This website is just like a start-ups idea. Recently only few competitors are
present in the Indian Market. Companies like cashkaro, topcashback, gopaisa,
coupondunia, grabon. These companies are providing cashback if we will buy
the same product listed on different website like amazom, flipkart . You have
to click on any product on cashkaro it will redirect you to amazon and inturn
you can get little amount of cash back.
\item Our BOOK SELLING WEBSITE is little bit similar to these companies.
If we want to purchase any book from any website then the same book is registered at different price at different website.
\item  Our website will display the same
book which is registered at cheapest price among all the website like amazon,
flipkart. We currently only deal with book because this is one of the major problem faced by various students either he/she is in college or in school. In this way
we solve one major problem of students. We will not charge any amount like
other companies amazon and flipkart to display their product on the website.
\end{itemize}
\newpage
{\Large\textbf{Objective of our Project}}
	\begin{itemize}
	    
	 \item For the first time, Buyer registers with the website to generate a valid
username and password.
\item  Login web page: Once the registration is successful, the buyer can login
and go for searching and shopping various products available.
\item After login, Buyer can view all the recommended products on the home page compiled by system based on users past shopping information and
other factors mentioned by the user.
\item  Search Option - Buyer can search for some products and select the desired
product and view its details and add to cart if he/she wishes to buy the
product.
\item  Buy Option – Once buyer will click on buy button he will be redirected to
Different shopping website on which the product is available at cheapest
price.
\item  Order Placing – After redirecting to that page buyer can purchase the
product and pay the required amount then product will be delivered to
his desired address
\item  Payment Method – Payment should be accepted on redirected website in
all format google pay, amazon pay, freecharge, net banking, debit card,
credit card, pay on delivery.

	\end{itemize}

\newpage
{\large\textbf{PROGRAMMING LANGUAGES AND SOFTWARES}}\\

{\large\textsc{FRONT END DEVELOPMENT}}
\begin{itemize}
    \item HTML5 Basic Design ,Layout and other feauters like forms,images ,buttons etc.
    \item Bootstrap CSS - For further styling and more enhancing and appealing look of the web pages used in software.
\end{itemize}
\vspace{15pt}
{\large\textsc{SERVER SIDE SCRIPTING LANGUAGE}}
\begin{itemize}
\item PHP -The scripting side language we have used,to interact with the database.
\end{itemize}
\vspace{15pt}
{\large\textsc{DATA BASE MANAGEMENT}}
\begin{itemize}
\item Using MySQL, we have been storing confidential data of the users securely and using it to provide them optimal services.
\end{itemize}
\vspace{15pt}
{\large\textbf{ROLES OF OUR TEAM MEMBERS}}
\begin{itemize}
\item \textbf{Manasa S}(200010058) : Implemented Graphic Designing and video Editing of Our Project
\item {\textbf{Karthik k}}(200010024) :Implemented front end by using HTML5 and Bootstrap CSS
\item \textbf{Rahul Raj}(200010044) : Implemented Back-end of our project using PHP and MySql
\end{itemize}
\vspace{15pt}
\newpage
{\large\textbf{IMPLEMENTATION OF FILES AND ROLES}}\\\\
As HTML5 and Bootstrap CSS are implemented in PHP files itself, we didn't split frontend and backend files
\begin{itemize}
\item index.php :This file is for whether a user has to sign up or login to a portal.
\item login.php :The file contains a user's login portal.
\item signup.php:The user has to create an account using this signup portal.
\item logout.php:The file contains a user's logout portal.
\item connection.php :In this file, we connect to a data base that we had developed a query for.
\item cart.php:This file includes  information about cart items if included and includes top sale selection
\item footer.php : This files is for footer(copyrights etc) of our website
\item header.php:This file is for header(login,cart,home,etc) of our website
\item index.js :
\item product.php :
\item index.js :
\item functions.php :
\end{itemize}
\end{document}
